Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-11 emsoft-2019/intro.tex

We have implemented our algorithm on top of Matlab's multi-parametric toolbox 
for robust explicit MPC \cite{Matlab-MPT?}
and the Daisy tool for multi-precision tuning and fixed-point error analysis \cite{Daisy}.
We have applied our technique on a number of standard benchmark examples.
Our implementation finds that our mixed-precision implementation can save up to 20\% memory (on average, XXX\%) in controller
implementations over a uniform-precision implementation (and a saving of XXX\% over a uniform 32-bit implementation), while
maintaining the correctness of the controller.
In absolute terms, the saving corresponds to YYY KB over a uniform precision implementation on our largest benchmark.
In each case, the analysis takes only a few minutes of computation.
We also demonstrate the scalability of our mixed-precision tuning and error bounds analysis:
we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes\todo{Hours?}.

>>>>

We have implemented our algorithm on top of Matlab's multi-parametric toolbox 
for robust explicit MPC~\cite{matlabMPT}
and the Daisy tool for multi-precision tuning and fixed-point error analysis \cite{Daisy}.
We have applied our technique on a number of standard benchmark examples.
Our implementation finds that our mixed-precision implementation can save up to 20\% memory (on average, XXX\%) in controller
implementations over a uniform-precision implementation (and a saving of XXX\% over a uniform 32-bit implementation), while
maintaining the correctness of the controller.
In absolute terms, the saving corresponds to YYY KB over a uniform precision implementation on our largest benchmark.
In each case, the analysis takes only a few minutes of computation.
We also demonstrate the scalability of our mixed-precision tuning and error bounds analysis:
we show that on explicit MPC controllers with thousands of regions, our tool finishes in a few minutes\todo{Hours?}.
